Matching Bullets

### 2015-11-24 imaging-paper.Rnw
Work in the discussion on the tilt of the lines

\hh{I'm putting in footnotes for URLs at the moment, they should probably be included properly in the references.}

@@

\begin{figure}[hbtp]
  \centering
\begin{subfigure}[b]{\linewidth}
\caption{View from the side.\label{fig:sidex3p}}{%
      \includegraphics[width=\linewidth]{images/sidex3p.png}
    }
\end{subfigure}    
\begin{subfigure}[b]{\linewidth}
    \caption{View from the top.\label{fig:topx3p}}{%
    \includegraphics[width=\linewidth]{images/topx3p.png}
    }
\end{subfigure}
\caption{An example of a scan of a bullet land from one groove to the next. }
\end{figure}
Each fired bullet is provided in form of a set of six x3p files, where each file is a surface scan between adjacent grooves on the bullet, called a ``land". An example of plotting one of these lands is given in Figures~\ref{fig:sidex3p} and~\ref{fig:topx3p}, which show side and top profiles of the land respectively.
\hh{The tilt of the lines to the left in Figure~\ref{fig:topx3p} is not an artefact, but a direct and expected consequence of the spin induced by the rifling during the firing process. Depending on whether a barrel is rifled clock-wise or anti-clockwise, the striations have a left or right tilt. The direction of the rifling is a class characteristic. XXX rotation in Ruger? twist rate?}

The primary goal in this type of forensic analysis is to identify markings. Gun barrels should produce similar markings on bullets fired consecutively, and the careful analysis of these surface images can help us determine whether two bullets are a match. However, this process has traditionally required forensic experts to perform the analysis, also required physical examination of the bullets. We've produced a framework which, in software, allows for the analysis of the surface topologies, and also transcribes the markings into a 2D plotting framework which we believe makes identification of matches easier for the lay person.

>>>>

@@

\begin{figure}[hbtp]
  \centering
\begin{subfigure}[b]{\linewidth}
\caption{View from the side.\label{fig:sidex3p}}{%
      \includegraphics[width=\linewidth]{images/sidex3p.png}
    }
\end{subfigure}    
\begin{subfigure}[b]{\linewidth}
    \caption{View from the top.\label{fig:topx3p}}{%
    \includegraphics[width=\linewidth]{images/topx3p.png}
    }
\end{subfigure}
\caption{An example of a scan of a bullet land from one groove to the next. }
\end{figure}
Each fired bullet is provided in form of a set of six x3p files, where each file is a surface scan between adjacent grooves on the bullet, called a ``land". An example of plotting one of these lands is given in Figures~\ref{fig:sidex3p} and~\ref{fig:topx3p}, which show side and top profiles of the land respectively. The tilt of the lines to the left in Figure~\ref{fig:topx3p} is not an artifact, but a direct and expected consequence of the spin induced by the rifling during the firing process. Depending on whether a barrel is rifled clockwise or counter-clockwise, the striations have a left or right tilt. The direction of the rifling is a class characteristic.

The primary goal in this type of forensic analysis is to identify markings in an attempt to match two bullets. Gun barrels should produce similar markings on bullets fired consecutively, and the careful analysis of these surface images can help us determine whether two bullets are a match. However, this process has traditionally required forensic experts to perform the analysis, also required physical examination of the bullets. We've produced a framework which, in software, allows for the analysis of the surface topologies, and also transcribes the markings into a 2D plotting framework which we believe makes identification of matches easier for the lay person.
